---
title: "Report 1"
date: "Last Updated: `r format(Sys.Date(), format = '%B %d, %Y')`"
knit: (function(inputFile, encoding) { rmarkdown::render(inputFile, encoding = encoding, output_file = paste0(substr(inputFile,1,nchar(inputFile)-4),"_",gsub("-", "", substring(Sys.Date(), 3)),'.html')) })
output:
  html_document:
    toc: true
    toc_depth: 4
    toc_float: true
      collapsed: false
---

```{r setup, include=FALSE}
# set chunk defaults
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
set.seed({{format(Sys.Date(), format = "%Y%m%d")}})

knitr::opts_chunk$set(fig.width=8, fig.height=10) 
```

```{r import, include=FALSE}
library(biostatR)
library(tidyverse)
library(captioner)

# setting MSK ggplot theme and color palette
theme_set(mskRvis::theme_biostat())
mskRvis::set_msk_palette()
{{(ifelse(tolower(Sys.info()[["user"]]) %in% eval(as.list(bstfun::theme_gtsummary_msk)$name), glue::glue("
# Set custom gtsummary theme if exists in the bstfun::theme_gtsummary_msk
bstfun::theme_gtsummary_msk('{tolower(Sys.info()[['user']])}')
"), ""))}}

# importing master analytic data set
df_master <-
  readRDS(
    file = here::here(path_data, "df_master.Rds")
  )

# Import analysis result objects here
load(here::here(path_data,"020-analysis.RData"))
```

```{r inline_text, include=FALSE, echo=FALSE}
# define complex inline-reporting objects here
```


```{r captions, include = FALSE}
## Setting up Table and Fig numberings ------------------
tbl_cap = captioner(prefix = "Table")
fig_cap = captioner(prefix = "Figure")

## table captions --------------
  tbl_cap("tab_table1", "Patient Characteristics")
  
## figure captions ------------------------------------
  fig_cap("fig_ROCgrade", "Grade ROC")
  
## To refer to table/fig in the text ------------------------------------
  # Function to reference table in text
  f.ref <- function(x) {
    stringr::str_extract(tbl_cap(x), "[^:]*")
  }
  # example: **`r table_nums("tab_table1", display = "cite")`**

  # Function to reference figure in text
  f.ref.fig <- function(x) {
    stringr::str_extract(fig_cap(x), "[^:]*")
  }
  # example: **`r f.ref("fig_ROCgrade")`**
```

*Output generated using the following dataset(s) received `r readr::read_lines(here::here("data_date.txt"), n_max = 1)`: ''*
 
# Methods

We analyzed `r n_distinct(df_master$EPISODE_ID)` prostate RO episodes from the [RO Episode file (2015-2017)](https://innovation.cms.gov/Files/x/rad-onc-data-dictionary.pdf) dataset.

The analysis objectives included: TO BE FILLED IN 

* Bullet 1 
* Bullet 2 
    + Bullet 2a 
    + Bullet 2b 
    
A significance level of 0.05 was used throughout.

All analyses were conducted using `r cite_r(pkgs = c("tidyverse", "gtsummary"), add_citation = TRUE)`.

# Results

## **`r tbl_cap('tab_table1')`**
```{r, table1}
```

<br>
<br>

# References

